---
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
resource_files:
- hh_crosswalk.csv
- Rad_Onc_Data.csv
- Radiology_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- hh_crosswalk.csv
- Radiology_Data.csv
- Rad_Onc_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- open_encounters_exclusion.xlsx
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>
```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 100000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```



```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)

access_raw_tbl <- tbl(conn1, "MV_DM_PATIENT_ACCESS")
radiology_tbl <- tbl(conn1, "RADIOLOGY_DATA")
rad_onc_tbl <- tbl(conn1, "RAD_ONC_DATA")
radiology_site_tbl <- tbl(conn1, "RADIOLOGY_SITE_MAPPING")
missing_enc_dept_tbl <- tbl(conn1, "OPEN_ENC_EXCLUSION_DEPT")
missing_enc_visit_tbl <- tbl(conn1, "OPEN_ENC_EXCLUSION_VISIT")
missing_enc_resource_tbl <- tbl(conn1, "OPEN_ENC_EXCLUSION_RESOURCE")
hh_crosswalk_tbl <- tbl(conn1, "HH_CROSSWALK") 

radiology_dep_mapping_tbl <- tbl(conn1, "RADIOLOGY_DEP_MAPPING")

```


```{r Global Functions, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))

```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

report_run_date <- Sys.Date()

todays_year <- year(Sys.Date())
prior_year <- year(Sys.Date())-1

date_start <- as.Date(paste0(year(Sys.Date())-1,"-01-01"))

# date_data <- access_raw_tbl %>%
#   filter(DERIVED_STATUS_DESC == "Arrived") %>%
#   group_by(CONTACT_DATE) %>%
#   summarise(total = n()) %>%
#   collect()

date_end <- as.Date(Sys.Date()-1)

date_start_formatted <- paste0(format(as.Date(date_start), "%Y-%m-%d"), " 00:00:00")
date_end_formatted <- paste0(format(as.Date(date_end), "%Y-%m-%d"), " 00:00:00")

monthOptions <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")

# Missing Charges Date Cutoff ------------------
business_days <- seq(date_start, date_end, by="days")[!is.weekend(seq(date_start, date_end, by="days"))]
missing_chg_cutOff <- business_days[length(business_days)-3] # Should this be 2 or 3?

```



```{r Scheduling Data Filtering, echo = FALSE, warning = FALSE, message = FALSE}

# scheduling_data <- access_raw_tbl %>%
#   dplyr::select(PAT_ENC_CSN_ID, CONTACT_DATE, APPT_STATUS_NAME,
#                 DEPARTMENT_ID, DEPARTMENT_NAME, DEPT_SPECIALTY_NAME,
#                 PROV_ID, PROV_NAME_WID, PRC_NAME, PRC_ID, APPT_MADE_DTTM,
#                 APPT_MADE_DATE, APPT_BLOCK_NAME, APPT_DTTM,
#                 APPT_CANC_DTTM, APPT_CANC_DATE,
#                 EM_CODE_YN, PAT_NAME,
#                 MRN, VISIT_GROUP_NUM,
#                 FINCLASS, VISITPAYOR, VISITPLAN,
#                 VISIT_PROV_STAFF_RESOURCE_C,
#                 VISIT_TYPE,
#                 NPI,
#                 CAMPUS,
#                 Y_COSIGN_MSG, Y_CHART_COSIGN_ID, COSIGN_NAME, Y_ENC_COSIGN_TIME, Y_ENC_CLOSE_TIME,
#                 Y_ENC_OPEN_TIME,
#                 COS_PROV_ID, COS_PROV_NAME,
#                 ENC_CLOSED_CHARGE_STATUS, PRIMARY_DX_CODE, PRIMARY_DX_NAME, LOS_CODE,
#                 LOS_NAME, DERIVED_STATUS_DESC, DEP_RPT_GRP_ELEVEN, DEP_RPT_GRP_SEVENTEEN,
#                 SITE, VISIT_METHOD, VIS_NEW_TO_DEP_YN, VIS_NEW_TO_PROV_YN, SCHED_METHOD)

```


```{r Scheduling Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

scheduling_data <- tbl(conn1, "MV_DM_PATIENT_ACCESS") %>%
  left_join(radiology_dep_mapping_tbl %>% select(DEPARTMENT_ID, DEP_CLASS),
            by = c("DEPARTMENT_ID")) %>%
  mutate(radiology_check = ifelse((DEP_CLASS == "OP") | (DEP_CLASS == "IP_OP" & PATIENT_CLASS %LIKE% '%OUTPATIENT%') | (DEP_CLASS == "IP_OP" & is.na(PATIENT_CLASS)), "Include", "Exclude")) %>%
  mutate(radiology_check = ifelse(is.na(radiology_check), "Include", radiology_check)) %>%
  filter(radiology_check == "Include") %>%
  filter(!is.na(SITE)) %>%
  mutate(Campus = SITE) %>%
  # mutate(Campus = case_when(DEPARTMENT_NAME %in% c("1176 5TH DUBIN MED ONC", "1176 5TH DUBIN SURG ONC") ~ "DUBIN",
  #                           DEPARTMENT_NAME %in% c("1468 MADISON CANCER", "1470 MADISON CANCER CENTER", "10 E 102ND ST INFUSION WHITE BAG", "THERAPEUTIC INF") ~ "RTC",
  #                           TRUE ~ SITE)) %>%
  filter(!Campus %in% c("MS NOW", "MSHP", "OTHER", "ONCOLOGY")) %>%
  mutate(Appt.DateYear = TO_DATE(CONTACT_DATE),
         Appt.Year = year(CONTACT_DATE),
         Appt.MonNum = month(CONTACT_DATE)) %>%
  mutate(Visit.Method  = ifelse(VISIT_METHOD == "IN PERSON", "IN PERSON", "TELEHEALTH"),
         New.PT3 = ifelse(is.na(LOS_NAME), NA, ifelse(LOS_NAME %like% "INITIAL|NEW", "New", "Established")),
         enc.status = ifelse(ENC_CLOSED_CHARGE_STATUS %in% c("OPEN", "CLOSED BUT COSIGN NEEDED"), 'OPEN', 'CLOSED')) %>%
  mutate(open.days = ifelse(enc.status == "OPEN",
                            TO_DATE(lubridate::today()) - TO_DATE(CONTACT_DATE),
                            TO_DATE(Y_ENC_CLOSE_TIME) - TO_DATE(CONTACT_DATE))) %>%
  mutate(Provider = trim(REGEXP_REPLACE(PROV_NAME_WID, "\\[.*?\\]", "" )))
```


```{r Open Encounters Metric Trending by Site 3, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

# EPIC Open Encounters Exclusion Criteria ---------------------------------
# missing_exc_dept <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_dept.xlsx")
# missing_exc_resource <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_res.xlsx")
# missing_exc_visitType <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_visit.xlsx")

missing_exc_dept <- missing_enc_dept_tbl %>% collect()
missing_exc_resource <- missing_enc_resource_tbl %>% collect()
missing_exc_visitType <- missing_enc_visit_tbl %>% collect()

exc_depts <- unique(missing_exc_dept$DEPARTMENT)
exc_providers <- unique(missing_exc_resource$PROVIDER)
exc_prc_name <- unique(missing_exc_visitType$PRC_NAME)
exc_prc_id <- unique(missing_exc_visitType$PRC_ID)

missing_chg_cutOff <- paste0(format(as.Date(missing_chg_cutOff), "%Y-%m-%d"), " 00:00:00")

missing_chg_data <- scheduling_data %>%
  filter(Appt.Year >= prior_year) %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  filter(VISIT_PROV_STAFF_RESOURCE_C == 1)

missing_chg_data <- missing_chg_data %>%
  filter(TO_DATE(missing_chg_cutOff,"YYYY-MM-DD HH24:MI:SS") >= TO_DATE(APPT_DTTM))

missing_chg_data <- missing_chg_data %>%
  mutate(clo.5days = ifelse(open.days <= 5, 'YES', 'NO')) %>%
  group_by(Campus, DEPARTMENT_NAME, Provider, PRC_NAME, PRC_ID, Appt.Year, Appt.MonNum, enc.status, clo.5days) %>%
  summarise(total = n()) %>%
  collect()

missing_chg_data <- missing_chg_data %>%
  filter(DEPARTMENT_NAME %!in% exc_depts) %>%
  filter(Provider %!in% exc_providers) %>%
  filter(PRC_NAME %!in% exc_prc_name) %>%
  filter(PRC_ID %!in% exc_prc_id) %>%
  filter(!str_detect(PRC_NAME, "ECHO|SOCIAL|NURSE|NUTRITION|LAB|TREATMENT")) %>%
  mutate(Appt.Month = format(as.Date(paste0(Appt.MonNum, "-01-", Appt.Year), "%m-%d-%Y"), "%b")) %>%
  mutate(Appt.Year = as.character(Appt.Year)) %>%
  mutate(Appt.MonthYear = paste0(Appt.Month,"-",Appt.Year))


missing_chg_data_trend_5days <- missing_chg_data %>%
  group_by(Campus, Appt.Year, Appt.MonNum, Appt.MonthYear, enc.status, clo.5days) %>%
  summarise(total = sum(total)) %>%
  group_by(Campus, Appt.Year, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  pivot_wider(names_from = clo.5days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.5days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")


missing_chg_data_trend_downtown_5days <- missing_chg_data %>%
  filter(Campus %in% c("MSUS","MSDMG","MSBI")) %>%
  mutate(Campus = "MS Downtown") %>%
  group_by(Campus, Appt.Year, Appt.MonNum, Appt.MonthYear, enc.status, clo.5days) %>%
  summarise(total = sum(total)) %>%
  group_by(Campus, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  pivot_wider(names_from = clo.5days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.5days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")


path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
saveRDS(missing_chg_data_trend_5days, paste0(path,"missing_chg_data_trend_5days.rds"))
saveRDS(missing_chg_data_trend_downtown_5days, paste0(path,"missing_chg_data_trend_downtown_5days.rds"))

# missing_chg_data_trend_5days <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/missing_chg_data_trend_5days.rds"))
# missing_chg_data_trend_downtown_5days <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/missing_chg_data_trend_downtown_5days.rds"))


```


```{r MSHS Unlocked Notes Metrics, echo = FALSE, warning = FALSE, message = FALSE}

missing_ytd_data <-scheduling_data %>%
  filter(Appt.Year == todays_year) %>%
  filter(DERIVED_STATUS_DESC == "Arrived")

missing_ytd_data <-missing_ytd_data %>%
  filter(VISIT_PROV_STAFF_RESOURCE_C == 1) %>%
  filter(TO_DATE(missing_chg_cutOff,"YYYY-MM-DD HH24:MI:SS") >= APPT_DTTM)

missing_ytd_data <-missing_ytd_data %>%
  mutate(clo.5days = ifelse(open.days <= 5, 'YES', 'NO')) %>%
  collect()


path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
saveRDS(missing_ytd_data, paste0(path,"missing_ytd_data.rds"))

invisible(gc())
```


```{r Manual Run of HH Data, echo = FALSE, warning = FALSE, message = FALSE}

path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
hh_data_comp_raw <<- read.csv("hand_hygiene_comp.csv")
saveRDS(hh_data_comp_raw, paste0(path,"hh_data_comp_raw.rds"))

hh_data_comp_raw_pt_entry <<- read.csv("pt_hand_hygiene_comp.csv")
saveRDS(hh_data_comp_raw_pt_entry, paste0(path,"pt_hand_hygiene_comp.rds"))

```

